Forecasting the 2024 Election: Trump Dominates the South, Harris Leads in the Midwest

### 2024-10-22 paper/paper.qmd
committing formatting and text changes to paper.qmd
committing text changes and cross references to paper.qmd

# Introduction

@@

The remainder of this paper is structured as follows. In Section 2, we describe the data and variables used in the analysis. Section 3 outlines the model setup and estimation strategy. Section 4 presents the results, including the predicted election outcomes and visualizations. Finally, Section 5 discusses the implications and limitations of our findings.

@@

## Summary of Predicted Election Results by State
@tbl-modelresults further breaks down the polling data by state, showing the average polling percentages for each candidate and the predicted win probability for Trump. For example, in Florida, Trump’s polling average is 53%, and his predicted win probability is almost certain at 99.93%. Conversely, in Michigan, Harris leads with an average of 46.27% of the vote, resulting in a 96.77% predicted probability that she will win the state.

In swing states like North Carolina and Nevada, where the polling percentages are closer, Trump is still predicted to win with probabilities of 94.36% and 51.23%, respectively. These battleground states show tighter polling averages and thus greater uncertainty in the predicted outcomes.
```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Predicted 2024 US Presidential Election outcomes by state, based on polling percentages for Trump and Harris"
#| warning: false

@@

### Confusion Matrix
[@tbl-confusion-matrix] displays the model's predictive performance in distinguishing between state-level wins for Trump (coded as 1) and Harris (coded as 0). In this case, the model correctly predicted 12 Harris wins and 15 Trump wins (true positives and true negatives). However, there were 5 instances where the model incorrectly predicted a Trump win when Harris won (false positives), and 3 instances where it predicted a Harris win when Trump won (false negatives). This breakdown helps assess not only the overall accuracy but also how well the model distinguishes between close contests in different states, which is critical for predicting the outcome of the 2024 presidential election.

@@

@@

Building on our discussion of the New York Times/Siena College Poll, we now present an idealized methodology that aims to enhance the accuracy and reliability of our predictions. This approach incorporates best practices and innovative techniques to ensure a comprehensive prediction of voter behavior in the upcoming 2024 U.S. presidential election. To demonstrate our idealized methodology, we generated a survey on the 2024 US Presidential election, which can be accessed via the the URL provided in [@sec-references] [@US-election-survey].

>>>>

# Introduction {#sec-introduction}

@@

The remainder of this paper is structured as follows. In [@sec-data], we describe the data and variables used in the analysis. [@sec-model] outlines the model setup and estimation strategy. [@sec-results] presents the results, including the predicted election outcomes and visualizations. Finally, [@sec-discussion] discusses the implications and limitations of our findings.

@@

## Summary of Predicted Election Results by State
@tbl-modelresults further breaks down the polling data by state, showing the average polling percentages for each candidate and the predicted win probability for Trump. For example, in Florida, Trump’s polling average is 53%, and his predicted win probability is almost certain at 99.93%. Conversely, in Michigan, Harris leads with an average of 46.27% of the vote, resulting in a 96.77% predicted probability that she will win the state. In swing states like North Carolina and Nevada, where the polling percentages are closer, Trump is still predicted to win with probabilities of 94.36% and 51.23%, respectively. These battleground states show tighter polling averages and thus greater uncertainty in the predicted outcomes.
```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Predicted 2024 US Presidential Election outcomes by state, based on polling percentages for Trump and Harris"
#| warning: false

@@

### Confusion Matrix
[@tbl-confusion-matrix] displays the model's predictive performance in distinguishing between state-level wins for Trump (coded as 1) and Harris (coded as 0).

@@

```
In this case, the model correctly predicted 12 Harris wins and 15 Trump wins (true positives and true negatives). However, there were 5 instances where the model incorrectly predicted a Trump win when Harris won (false positives), and 3 instances where it predicted a Harris win when Trump won (false negatives). This breakdown helps assess not only the overall accuracy but also how well the model distinguishes between close contests in different states, which is critical for predicting the outcome of the 2024 presidential election.

@@

Building on our discussion of the New York Times/Siena College Poll, we now present an idealized methodology that aims to enhance the accuracy and reliability of our predictions. This approach incorporates best practices and innovative techniques to ensure a comprehensive prediction of voter behavior in the upcoming 2024 U.S. presidential election. To demonstrate our idealized methodology, we generated a survey on the 2024 US Presidential election, which can be accessed via the the URL provided in [@US-election-survey] under [@sec-references].
